---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SmoothOperator

<!-- badges: start -->
<!-- badges: end -->

> Easy Feature Engineering with mgcv Penalized Spline Smooths

A convenient API for working with penalized spline smooths, based on the mgcv package. The smooths can easily be integrated with user-defined models and algorithms.

## Installation

You can install the development version of SmoothOperator from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hriebl/SmoothOperator")
```

## Example

Define and construct a simple cubic regression spline:

```{r example1}
library(SmoothOperator)
set.seed(1337)

df <- data.frame(x = runif(100))
smt <- Smooth$new("x", df, bs = "cr", k = 10)
smt

mat <- smt$construct()
str(mat)
```

Initialize and inspect knots and constraints:

```{r example2}
smt$initialize_knots()
smt$knots

# adds an explicit centering constraint
smt$initialize_constraints()
smt$constraints

pc <- data.frame(x = 0.5)
smt$add_point_constraints(pc)
smt$constraints
```
